Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-02-14 manuscript/bef_stability/manuscript.Rmd
Begin to explain SEM hypothesis

We built a metamodel to set up the nodes and the links between the different
compartment of the SEM. Basically, we wanted to test the links between
environmental conditions, community structure and stability. Theory in ecology 
predicts that community structure influences stability. In turn, environment 
influences community structure but also directly stability.

To characterize environment, we retained five axis of PCA on habitat and
climatic variables which represent different types of forcing (constant and
variability). The two first axis (RC1 and RC2) were mainly linked the physical
structure and position of the river and the altitutinal gradient (+temperature).
The third axis (RC3) was linked to enrichment (Organic Biological Demand) and CV
of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
environmental variability, respectively to CV of width and depth of the river
and CV of enrichment.

- Community structure:
  - species richness:
  - avg trophic level:
  - connectance:
  - beta diversity:

- Stability:
  - 2 components synchrony and $CV_{sp}$

The stream physical structure (RC1 axis) and its altitutinal position (RC2 axis)
was linked to species richness [REF].

@@

>>>>

We built a metamodel to set up the nodes and the links between the different
compartment of the SEM. Basically, we tested the links between
environmental conditions, community structure and stability. Theory in ecology 
predicts that community structure influences stability. In turn, environment 
influences community structure but also directly stability.

#### Variables

To characterize environment, we retained five axis of PCA on habitat and
climatic variables which represent different types of forcing (constant and
variability). The two first axis (RC1 and RC2) were linked to the physical
structure and position of the river and the altitutinal gradient (+temperature).
The third axis (RC3) was linked to enrichment (Organic Biological Demand) and CV
of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
environmental variability, respectively to CV of width and depth of the river
and CV of enrichment.

The community structure was characterized by total species richness (TSR),
species turnover (ST), median average weighted trophic level (TLvl) and median connectance.
Total species richness was the number of unique fish species that were observed
at a given station over the whole sampling. Species turnover was computed as average
dissimilarity between the different community composition through time. The
dissimilarity was calculated on species presence/absence with the Bray-Curtis
method implemented in the `vegan` R package (`vegdist` function). Both median
connectance and Tlvl were just computed as the median over the temporal period.
For the details of the computation of the trophic networks, see Network
inference part.

The biomass stability was decomposed in synchrony and weighted average CV
components according to @thibaut_understanding_2013.

#### Causal relationships

---
# Environment to community attributes and stability  
---
We linked environmental variables both to community structure and stability
components. Rooted in assembly theory, environment filters species that can
establish in a community and thus affect community structure. (+ add specific
hypothesis about physical and climate). (1) We hypothesized that enrichment
(characterized by DBO) and mean annual temperature will increase ST
[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
decrease biomass stability directly without going by community structure. First,
instability of habitat and environmental factors may in turn drive biomass
instability [@hansen_climate_2013]. Secondly, average environmental conditions
such as enrichment can increase directly CV by increasing species biomass
fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
to decrease stability through starvation resulting from high metabolic activity
[@tabi_warming_2019].

---
# Species richness to community attributes 
---
The reveal the mechanisms behind the relationship between species richness and
biomass stability, causal links were set from species richness to other
community attributes. (4) We hypothesized that TSR increased ST because
increasing species richness because of assembly processes. Species rich
community are more resistant to invasion and thus produces more ST
[@tilman_niche_2004; @shurin_how_2007].

@@

- Stability versus several studies:
  - [@zhang_scale_nodate]: productivity stability range from [0.4 to 1.4] for
    diversity range [10 to 30]
  - [@tilman_biodiversity_2006] on abundances:
    - stability range: 2 to 12
    - diversity range: 1 to 16
